Meesters TODO List

### 2023-03-22 files/Chapter2/generalvibrationmodel.tex
Partial work

\newtheorem*{Poincare_2}{Corollary}
\begin{Poincare_2}
	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$.
\end{Poincare_2}
\begin{proof}
	\textcolor{red}{Inlas 41A. Inlas 41B. Theorem 1.}
\end{proof}

There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
\begin{proof}
	Let $f \in V$, then $f_1(0) = f_2(0) = 0$. Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following inequality for the norm $||\cdot||_X$ can be obtained.
	\begin{eqnarray*}
		||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
		& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
		& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
	\end{eqnarray*}

@@

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1. \textcolor{red}{******* WHY NOT T-2???}\\

@@

The solution to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.\\

Kan sien met substituting, meer

MODAL solution\\

@@

Simple substitution confirms that the trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\

As w en phi kan 2.4.1 en () dan sal .... nie nodig nie. Probeer so ver as moontlik nie seperation of variables gebruik nie. Se eerder oof w en phi is sin en cos\\

@@

\subsection{General vibration problem new}
\subsection{General vibration problem old}

>>>>

\newtheorem*{Poincare_2}{Corollary}
\begin{Poincare_2}
	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$.
\end{Poincare_2}
\begin{proof}
	\textcolor{red}{Inlas 41A.}
\end{proof}

\newtheorem{Theorem_1}{Theorem}
\begin{Theorem_1}
There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
\end{Theorem_1}

\begin{proof}
	Let $f \in V$, then $f_1(0) = f_2(0) = 0$. Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following inequality for the norm $||\cdot||_X$ can be obtained.
	\begin{eqnarray*}
		||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
		& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
		& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
	\end{eqnarray*}

@@

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.\\

@@

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are modal solutions of the differential equations and satisfy the boundary conditions.\\

@@

@@

\subsection{General vibration problem new}
In the previous section In this subsection, is an investigation of the validity of a series solution for a general vibration problem. Specifically, the validity of the series solution given some initial conditions.\\

\subsection{General vibration problem old}
